Integration of Multiple Constraints in ACG

### 2013-07-17 lenls/abstract.tex
LENLS: More feedback and back to 4p

\setlength{\droptitle}{-13em}

@@

\title{An Integration of Multiple Constraints in ACG}
\author{Jiří Maršík \and Maxime Amblard}
\maketitle

\begin{abstract}
  We present work whose ultimate goal is the creation of a wide-coverage
  abstract categorial grammar (ACG) that could be used to automatically
  build discourse-level representations. We focus on the challenge of
  integrating the treatment of disparate linguistic constraints in a
  single ACG and propose a generalization of the formalism: graphical
  abstract categorial grammars.
\end{abstract}

@@

Abstract categorial grammars (ACGs) have shown to be a viable formalism
for elegantly encoding the dynamic nature of discourse. Proposals based
on continuation semantics \cite{de2006towards} have tackled topics such
as event anaphora \cite{qian2011event}, SDRT discourse structure
\cite{asher2011sdrt} and modal accessibility constraints
\cite{asher2011montagovian}. However, all of these treatments only
consider tiny fragments of languages. We are interested in building a
wide-coverage grammar which integrates and reconciles the existing
formal treatments of discourse and allows us to study their interactions
and to build discourse representations automatically.

In this paper we focus on the problem of constructing a wide-coverage
ACG. We identify a problem that comes up when one tries to enforce
multiple constraints/dependencies in a single ACG and we propose a
generalization of the formalism which allows for a natural solution to
the problem.

@@

This creates two problems. Firstly, the number of such types grows
exponentially with the number of features added. This can be fixed by
introducing dependent types into the type system as in
\cite{de2007type}. However, secondly, and perhaps more importantly, we have
lost the clarity and simplicity of describing the individual phenomena
independently. This makes adding new constraints more and more cumbersome and
reduces our capability to reason about our grammar. It no longer becomes
apparent which language mechanisms behave independently and their interactions
are hard to track. We firmly believe that simplicity is a fundamental
requirement for constructing a large and robust grammar and our proposal aims
to reclaim that simplicity.

In our grammar, we would like to combine several constraints
(Figure~\ref{fig:acg-comp-constr}) and possibly to also separate the syntactic
ambiguities from the purely semantic ones (Figure~\ref{fig:acg-comp-sem}).
However, these combinations are not possible in the framework of ACGs without
introducing complexity by solving all the constraints in one single type
signature (the consequences of we saw above) or contaminating the
syntax-semantics interface by the implementation details of the syntactic
layer.

We would like to have a system which would be characterized by a diagram like
the one on Figure~\ref{fig:gacg}. However, ACG diagrams are limited to
arborescences and we are obliged to generalize the formalism in order to get
the expected interpretation of Figure~\ref{fig:gacg}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth,height=0.2\textheight]{../diagrams/final.pdf}
  \caption{{\label{fig:gacg} A graphical ACG that implements two
      independent syntactic constraints and distinguishes syntactic and
      semantic ambiguities.}}
\end{figure}

We define a \emph{graphical abstract categorial grammar} as a directed
acyclic graph (DAG) whose nodes are labeled with signatures (and
distinguished types) and whose edges are labeled with lexicons, in other
words just a mathematical reification of an ACG diagram that has also
been generalized from arborescences to DAGs. We then search for an
appropriate semantics for these structures, i.e. how to determine what
languages are defined by a graphical ACG.

@@

G-ACG extrinsic languages correspond to ACG object languages with
intersection. More formally, it can be said that ACG object languages are just
ACG abstract languages closed on transformation by a lexicon, and we then show
that G-ACG extrinsic languages are just ACG abstract languages closed on
transformation by a lexicon and intersection.

@@

In the new paradigm, we interpret the nodes of the graph as terms and the
edges as statements that one term is mapped into another using a lexicon. This
leads us to the definition of the \emph{pangraphical} language of a node $u$
in a G-ACG $\mathcal{G}$.

@@

Finally, we construct a G-ACG which integrates the French negation
constraint discussed in Section~\ref{sec:constraints}, the constraints
on extraction introduced in \cite{pogodalla2012controlling} and a
constraint handling agreement in a single grammar specification. The
negation constraint is implemented exactly as was described in
Section~\ref{sec:constraints} and the extraction constraints are taken
``as is'' from \cite{pogodalla2012controlling}. The underlying syntactic
signature is defined without any concern for the additional constraints
and the syntax-semantics interface is kept simple as well.

In the end, this lets us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$,
$NP$ and $S$) and then define the constraints themselves the same way as
they are defined in papers which try to formalize them individually
(such as the case with \cite{pogodalla2012controlling}). We can also
freely combine both the constraint pattern and the syntax-semantics
ambiguities pattern from Section~\ref{sec:acg-comp}.

@@

We have considered the problem of building a wide-coverage ACG, specifically
the problem of expressing a multitude of linguistic constraints. We have
examined previous techniques and found no satisfying solution. We have thus
provided an extension of the ACG formalism to solve the problem and justified
the need for the increased expressivity.

>>>>

\setlength{\droptitle}{-14em}
\title{Integration of Multiple Constraints in ACG}
\date{\vspace{-5em}}

@@

\maketitle

This proposal is a first step towards a wide-coverage Abstract Categorial
Grammar (ACG) that could be used to automatically build discourse-level
representations. We focus on the challenge of integrating the treatment of
disparate linguistic constraints in a single ACG and propose a generalization
of the formalism: Graphical Abstract Categorial Grammars.

@@

Abstract Categorial Grammars (ACGs) have shown to be a viable formalism for
elegantly encoding the dynamic nature of discourse. Proposals based on
continuation semantics \cite{de2006towards} have tackled topics such as event
anaphora \cite{qian2011event}, SDRT discourse structure \cite{asher2011sdrt}
and modal accessibility constraints \cite{asher2011montagovian}. However, all
of these treatments only consider tiny fragments of languages. We are
interested in building a wide-coverage grammar which integrates and reconciles
the existing formal treatments of discourse and allows us to study their
interactions and to build discourse representations automatically.

In this paper we focus on the problem of constructing a wide-coverage ACG. We
identify a problem that comes up when one tries to enforce multiple
constraints/dependencies in a single ACG and we propose a generalization of
the formalism which resolves to the issue.

@@

This creates two problems. Firstly, the number of such types grows
exponentially with the number of features added. This can be fixed by
introducing dependent types into the type system as in
\cite{de2007type}. However, while this allows us to abstract over the
combinations of feature values and write our grammar down concisely, it does
not take away the complexity. The treatments of the various linguistic
phenomena are all expressed in the same types making it hard to see whether
they are independent or not. Since the treatments cannot be considered in
isolation, reasoning about the entire grammar becomes difficult and so does
enhancing it with more constraints. This is a fatal problem for a grammar
which strives to cover a wide range of linguistic facts. We firmly believe
that simplicity is a fundamental requirement for constructing a large and
robust grammar and our proposal aims to reclaim that simplicity.

In our grammar, we would like to combine several constraints
(Figure~\ref{fig:acg-comp-constr}) and possibly to also separate the syntactic
ambiguities from the purely semantic ones (Figure~\ref{fig:acg-comp-sem}).
However, trying to mix these strategies in the ACG framework forces us to
solve all the constraints in a single type signature or contaminate the
syntax-semantics interface with the implementation details of the syntactic
layer, both of which introduce incidental complexity we want to avoid.

We would like to have a system which would be characterized by a diagram like
the one on Figure~\ref{fig:gacg} where the constraint signatures delimit the
legal syntactic structures independently of each other and without interfering
with the syntax-semantics interface. However, ACG diagrams are limited to
arborescences and we are obliged to generalize them in order to get
the expected interpretation of Figure~\ref{fig:gacg}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.25\textwidth,height=0.2\textheight]{../diagrams/final.pdf}
  \caption{\label{fig:gacg} A graphical ACG that implements two
      independent syntactic constraints and distinguishes syntactic and
      semantic ambiguities.}
\end{figure}

We define a \emph{graphical abstract categorial grammar} as a directed acyclic
graph (DAG) whose nodes are labeled with signatures (and distinguished types)
and whose edges are labeled with lexicons, in other words a mathematical
reification of an ACG diagram that has been generalized from
arborescences to DAGs. We then search for an appropriate semantics for these
structures, i.e. how to determine what languages are defined by a graphical
ACG.

\subsection{Nodes as Languages}

@@

G-ACG extrinsic languages correspond to ACG object languages with
intersection. More formally, while ACG object languages are ACG abstract
languages closed on transformation by a lexicon, G-ACG extrinsic languages are
ACG abstract languages closed on transformation by a lexicon and intersection.

@@

\subsection{Nodes as Terms}

In the new paradigm, we interpret the nodes of the graph as terms and the
edges as statements that one term is mapped into another using a lexicon. This
leads us to the definition of the \emph{pangraphical}\footnote{As opposed to
  extrinsic languages, which are constrained only by their predecessors in the
  graph, pangraphical languages are constrained by the entire graph.} language
of a node $u$ in a G-ACG $\mathcal{G}$.

@@

Finally, we construct a G-ACG which integrates the French negation constraint
discussed in Section~\ref{sec:constraints}, the constraints on extraction
introduced in \cite{pogodalla2012controlling} and a constraint handling
agreement in a single grammar specification. The constraints are implemented
exactly as they were originally described. The underlying syntactic signature
is defined without any concern for the additional constraints and the
syntax-semantics interface is kept simple as well.

@@

We have considered the problem of building a wide-coverage ACG, specifically
the problem of expressing a multitude of linguistic constraints. We have
examined previous techniques and found no satisfying solution. We have thus
provided an extension of the ACG formalism to solve the problem and justified
the need for the increased expressivity. This embedding of syntactic
constraints will be used to define a syntax-semantics interface and then to
build discourse structures.

In the end, this lets us define the syntax in a clean way using the
idiomatic style of categorial grammars (simple atomic types like $N$,
$NP$ and $S$) and then define the constraints themselves the same way as
they are defined in papers which try to formalize them individually
(such as the case with \cite{pogodalla2012controlling}).
